Issues with Dynamical Measurements Across the Disk

### 2019-03-18 paper/ms.tex
Small fixes
Small changes to table comparing MW and simulation values, and minor updates to references

For a systematic offset in $z$ ({\em upper} panels), the
95\textsuperscript{th} minus 5\textsuperscript{th} percentiles are $2.2$ and
$6.2\,\actunit$ for $J_r$ and $J_z$, respectively. These are fractional errors
of $5.7\,\%$ and $85.7\,\%$, respectively. The error induced in $L_z$ is
negligible, as expected since $L_z$ is independent of $z$. It is worth
pointing out that a $100\,\pc$ error in an orbit with
$z_{\text{max}}=850\,\pc$ --- a $12\%$ error
--- induced a $43\%$ error in the computation of $J_z$.

@@

\begin{deluxetable*}{cccccc}
\tablecaption{Stellar disk scale heights of the real Milky Way and the
simulated galaxies considered in this work.\label{tab:scale_height}}
\tablehead{\colhead{galaxy} & \colhead{cold\tablenotemark{a} gas disk} & \colhead{stellar thin disk} & \colhead{stellar thick disk} & \colhead{cold gas softening length} & \colhead{stellar softening length} \\ 
\colhead{} & \colhead{(pc)} & \colhead{(pc)} & \colhead{(pc)} & \colhead{(pc)} & \colhead{(pc)} } 
\startdata
MW\tablenotemark{b} & 40 & 300 & 900 & 0 & 0 \\
\mi\tablenotemark{c} & 800\tablenotemark{d} & 480 & 2000 & 12.4 & 11.2 \\
\mf\tablenotemark{c} & 360 & 440 & 1280 & 12.5 & 11.2 \\
\mm\tablenotemark{c} & 250 & 290 & 1030 &10.3 & 11.2 \\
\enddata
% \tablerefs{\citet{2016ARAA..54..529B,2018arXiv180610564S,2008ApJ...673..864J}}
\tablenotetext{a}{$T<1000$ K}
\tablenotetext{b}{\citet{2008ApJ...673..864J,2016ARAA..54..529B}}
\tablenotetext{c}{\citet{2018arXiv180610564S}}
\tablenotetext{d}{The azimuthally averaged gas vertical density profile in
m12i is nearly constant to this height, though individual regions show smaller
scale heights and dense clouds.}
\end{deluxetable*}

>>>>

For a systematic offset in $z$ ({\em upper} panels), the
95\textsuperscript{th} minus 5\textsuperscript{th} percentiles are $2.2$ and
$6.2 \actunit$ for $J_r$ and $J_z$, respectively. These are fractional errors
of $5.7\%$ and $85.7\%$, respectively. The error induced in $L_z$ is
negligible, as expected since $L_z$ is independent of $z$. It is worth
pointing out that a $100\,\pc$ error in an orbit with
$z_{\text{max}}=850\,\pc$ --- a $12\%$ error
--- induced a $43\%$ error in the computation of $J_z$.

@@

\begin{deluxetable*}{cccccc}
\tablecaption{Stellar disk scale heights of the real Milky Way and the
simulated galaxies considered in this work.\label{tab:scale_height}}
\tablehead{\colhead{galaxy} & \colhead{cold\tablenotemark{a} gas disk} & \colhead{stellar thin disk} & \colhead{stellar thick disk} & \colhead{cold gas softening length} & \colhead{stellar softening length} \\ 
\colhead{} & \colhead{(pc)} & \colhead{(pc)} & \colhead{(pc)} & \colhead{(pc)} & \colhead{(pc)} } 
\startdata
MW\tablenotemark{b} & 40 & 300 & 900 & \nodata & \nodata \\
\mi\tablenotemark{c} & 800\tablenotemark{d} & 480 & 2000 & 12.4 & 11.2 \\
\mf\tablenotemark{c} & 360 & 440 & 1280 & 12.5 & 11.2 \\
\mm\tablenotemark{c} & 250 & 290 & 1030 &10.3 & 11.2 \\
\enddata
% \tablerefs{\citet{2016ARAA..54..529B,2018arXiv180610564S,2008ApJ...673..864J}}
\tablenotetext{a}{$T<1000$ K}
\tablenotetext{b}{\citet{2008ApJ...673..864J,2016ARAA..54..529B}}
\tablenotetext{c}{\citet{2018arXiv180610564S}}
\tablenotetext{d}{The azimuthally averaged gas vertical density profile in
m12i is nearly constant to this height, though individual regions show smaller
scale heights and dense clouds.}
\end{deluxetable*}
